A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-28 03_smoothing_tracks.Rmd

# prepare a palette
pal <- RColorBrewer::brewer.pal(3, "PRGn")
```

@@

```{r}
# prepare data to plot
# make list of data to plot
figure_median_smooth <-
  ggplot()+
  geom_point(data = data_errors,
             aes(x, y),
             col = pal[3],
             size = 0.2, alpha = 0.5)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            lwd = 0.5)+          
  geom_path(data = data_plot,
            aes(x, y,
                col = window_size,
                group = window_size),
            show.legend = F,
            lwd = 0.5)+
  coord_equal(expand = F,
              ylim = c(0.6, 0.85),
              xlim = c(NA, 2.3),
              ratio = 1.75)+
  annotate(geom = "text",
           x = c(0.75, seq(1.1, 2, length.out = 4)),
           y = 0.82,
           label = sprintf("(%s)", letters[seq(5)]),
           fontface = "bold")+
  scale_colour_distiller(palette = "BuPu", direction = 1,
                         values = c(-0.5, 1))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "white"))

@@

# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg)+
  geom_hline(yintercept =
               1 + quantile(data$speed, na.rm = T,
                        probs = c(0.5, 0.95)),
             lty = c(1, 2))+
  geom_errorbar(data = speed_agg_smooth,
                aes(x = factor(interval),
                    ymin = 1 + median - sd,
                    ymax = 1 + median + sd),
                width = 0.2,
                position = position_nudge(x = 0.25)) +
  geom_point(data = speed_agg_smooth,
             aes(x = factor(interval),
                 y = 1 + median),
             shape = 21,
             size = 3,
             fill = pal[3],
             position = position_nudge(x = 0.25)) +
  geom_boxplot(aes(factor(interval), 1 + speed),
               position = position_nudge(x = -0.25,),
               fill = pal[2],
               alpha = 0.5,
               show.legend = F, 
               width = 0.25, 
               outlier.size = 0.2)+
  scale_y_log10(label = scales::comma,
                limits = c(NA, 1.005))+
  ggthemes::theme_few()+
  theme(axis.text.y = element_blank())+
  labs(x = "interval (s)",
       y = "speed")
```

>>>>

# prepare a palette
pal <- RColorBrewer::brewer.pal(4, "Set1")
```

@@

```{r}
# prepare data to plot
# make list of data to plot
figure_median_smooth <-
  ggplot()+
  geom_point(data = data_errors,
             aes(x, y),
             col = pal[3],
             size = 0.2, alpha = 0.5)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            lwd = 0.5)+          
  geom_path(data = data_plot,
            aes(x, y,
                col = window_size,
                group = window_size),
            show.legend = F,
            lwd = 0.5)+
  coord_equal(expand = F,
              ylim = c(0.6, 0.85),
              xlim = c(NA, 2.3),
              ratio = 1.75)+
  annotate(geom = "text",
           x = c(0.75, seq(1.1, 2, length.out = 4)),
           y = 0.82,
           label = sprintf("(%s)", letters[seq(5)]),
           fontface = "bold")+
  scale_colour_distiller(palette = "BuPu", direction = 1,
                         values = c(-0.5, 1))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())

@@

# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg)+
  geom_hline(yintercept =
               1 + quantile(data$speed, na.rm = T,
                        probs = c(0.5, 0.95)),
             lty = c(1, 2))+
  geom_errorbar(data = speed_agg_smooth,
                aes(x = factor(interval),
                    ymin = 1 + median - sd,
                    ymax = 1 + median + sd),
                width = 0.2,
                position = position_nudge(x = 0.25)) +
  geom_point(data = speed_agg_smooth,
             aes(x = factor(interval),
                 y = 1 + median),
             shape = 21,
             size = 3,
             fill = pal[3],
             position = position_nudge(x = 0.25)) +
  geom_boxplot(aes(factor(interval), 1 + speed),
               position = position_nudge(x = -0.25,),
               fill = "grey",
               alpha = 0.5,
               show.legend = F, 
               width = 0.25, 
               outlier.size = 0.2)+
  scale_y_log10(label = scales::comma,
                limits = c(NA, 1.005))+
  ggthemes::theme_few()+
  theme(axis.text.y = element_blank())+
  labs(x = "interval (s)",
       y = "speed")
```
